\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-28 syntax.tex
comment

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, \cL \sigma_2'}{t}{T}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}
$$
$$
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\quad 
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$

@@

Finally we introduce the inheritance judgement. Inheritance are judgement so naturally second class citizen data (i.e. not something function can return and cannot be assigned to variables), and it looks very much alike a function that transform a given linkage.

The syntax of the inheritance judgement is very close to how Family is defined in the surface syntax---a Family with no parent is an inheritance with empty input; an extended Family is exactly an inheritance---because the parent of an extended Family can be overridden thus inheritance should only define upon the ``interface'' instead of a concrete family. However, since our current formulation doesn't support further-binding (i.e. we cannot do inheritance inside a family), our formulation still have some distance to the real family polymorphism.

"inhid" and "inhext" are simple as expected---the former corresponds to empty inheritance, and the latter gives the programmer the ability to add new field.

"inhinh" is special because it requires user to provide a proof of ``upcasting'' from the context of the children to that of the parent. In other words, if I want to inherit a specific field from the parent, I have to convince the type checker that my current context can ``accommodate'' the inherited field.

>>>>

$$
\Rule[name=Inh-Ext]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
  \quad \goodTerm{\Gamma, \cL \sigma_2'}{t}{T}\YZ{What is sigma2'?}}
{\goodInh{\Gamma}{"inhext" \ h \ t}{\sigma_1}{(\nu^+ \  \sigma_2\  T)}}
\quad
\Rule[name=Inh-Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodType{\Gamma, A_1}{T}{}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
}
{\goodInh{\Gamma}{"inhinh" \ h}{(\nu^+ \  \sigma_1 \  T)}{(\nu^+ \  \sigma_2 \  T[(\pi_1, \uparrow^s)])}}
$$
$$
\Rule[name=Inh+Inh]
{\goodInh{\Gamma}{h}{\sigma_1}{\sigma_2}
\quad \goodTerm{\Gamma, A_2}{\uparrow^s}{A_1[\pi_1]}
\quad 
\goodInh{\Gamma, A_2}{i}{\tau_1[(\pi_1, \uparrow^s)]}{\tau_2}}
{\goodInh{\Gamma}{"inhnest" \ h \ i}{(\nu^+ \  \sigma_1\  \cL\tau_1)}{(\nu^+ \  \sigma_2\  \cL\tau_2)}}
\quad
$$

@@

Finally we introduce the inheritance judgement. Inheritance are
judgement so naturally second class citizen data (i.e. not something
function can return and cannot be assigned to variables), and it looks
very much like a function that transform a given linkage.

The syntax of the inheritance judgement is very close to how Family is
defined in the surface syntax---a Family with no parent is an
inheritance with empty input; an extended Family is exactly an
inheritance---because the parent of an extended Family can be overridden
thus inheritance should only define upon the ``interface'' instead of a
concrete family. However, since our current formulation doesn't support
further-binding (i.e. we cannot do inheritance inside a family), our
formulation still has some distance to the real family polymorphism.

"inhid" and "inhext" are simple as expected---the former corresponds to
empty inheritance, and the latter gives the programmer the ability to
add new fields.

"inhinh" is special because it requires user to provide a proof of
``upcasting'' from the context of the child to that of the parent.
In other words, if I want to inherit a specific field from the parent, I
have to convince the type checker that my current context can
``accommodate'' the inherited field.
